### 2014-12-31 branches/kevin/docs/targetdp.tex
brnach update passin tests
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@2574 40876441-3496-0410-a613-a2fca35b2ae2

@@

There are three types of memory requirement we will consider.
(A fourth, constant host memory not suitable for target constant
memory is could also be handled, but is less likely to occur.)
An approach to each relevant type is set out in the three following
sections.

@@

\end{lstlisting}
Here, an implementation with either uniform or separate address
spaces must arrange a copy of the data at appropriate times so
that any updates to \texttt{host} are correctly reflected
in \texttt{target}. All kernel-related references are again through
\texttt{target}.
The slightly disjoint nature of this definition and increased pressure
on global name-space must be weighed against potential increase in kernel
performance and reduction in register pressure.

\subsubsection{Non \texttt{const} object in both address spaces}

The most general case may be handled in the following manner:
\begin{lstlisting}

struct object_kernel_data {
  ...
};

struct object {
   struct object_kernel_data * host;
   struct object_kernel_data * target;
   ...
};

\end{lstlisting}
All relevant kernel data may then be handled by references to
\texttt{target} in a consistent way. For implementations with
separate address spaces, the memory coherency issue
must be handled explicitly as both \texttt{host} and \texttt{target}
are subject to modification. However, an implementation with uniform
address space may simply alias the \texttt{target} to the \texttt{host}
pointer. No data reside at file scope.

>>>>

\subsubsection{Error handling}

The targetDP interface should provide a mechanism for errors to be
handled by the application.

@@

First, we consider the general problem of encapsulation of objects
in the context of device memory. We then consider two special cases
involving device constant memory.

\subsubsection{General}

It is useful to manage host and device memory in such a way that
three is a uniform interface to related functionality, and that
will not require substantially different code or API to handle the cases of
unified and separate address spaces.

The model used is to define host objects which include a reference
to an object of the same type intended for device memory. A schematic
example is
\begin{lstlisting}
struct object_s { 
  ...                            /* data items (host) */
  struct object_s * target;      /* device copy */
};
\end{lstlisting}
The object created on the host is then responsible for the management
of the appropriate device reference \texttt{target}. For implementations
with a unified address space the host may simply alias the target
reference to itself. For implementations with separate address spaces
appropriate allocation of device memory must be arranged, along with
necessary marshalling of data between host and device. The model
allows consistent use of functions with contract
\begin{lstlisting}
__host__ __device__ int object_function(struct object_s * obj, ...)
\end{lstlisting}
Kernel functions may be declared with contract
\begin{lstlisting}
__target_entry__ void object_kernel(struct object_s * obj, ...)
\end{lstlisting}
and must take the \texttt{target} reference as actual argument when invoked
from the host. Likewise, functions declared with \texttt{\_\_host\_\_}
attribute may be
invoked on the host with the
host reference as actual argument.
We note:
\begin{enumerate}
\item
A number of data items only relevant on the host may be retained in
the \texttt{target} reference redundantly.
\item
The \texttt{target} reference in the device copy is also redundant.
\item
The host does not maintain a permanent copy of all device memory
references in this model. However, these may be recovered from the
device if needed.
\end{enumerate}
I think the benefits this model, which allows a clearly uniform picture
of host and device memory, and is largely transparent to details of the
address space, justify the small number of slightly inelegant redundancies.

@@

\end{lstlisting}
Here, an implementation with either uniform or separate address
spaces must arrange a copy of the data at appropriate times so
that any updates to \texttt{host} are correctly reflected
in \texttt{target}. All kernel-related references are again through
\texttt{target}.
The slightly disjoint nature of this definition and increased pressure
on global name-space must be weighed against potential increase in kernel
performance and reduction in register pressure. More seriously, thre is
no way to write consistent \texttt{\_\_host\_\_ \_\_target\_\_} functions
(we can see) except to move the host structure back to file scope to
match the situation in the previous section.
